\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-31 Latex/paper.tex
# last version i have to end cms section

@@

D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right). 

@@

Now from (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that

@@

\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)

@@

Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future

@@

\begin{align}\label{ca_approximation_futures}
CA(t,t_0,t_1)& \nonumber \\ 
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
\end{align}

@@

\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that, we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Therefore, we can get the next approximation
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
\begin{equation*}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation*}
Therefore we have that

\hspace{2cm}
\fboxsep1em
\fbox{\parbox{335pt}
{
\begin{equation}\label{convexity_ois_future}
\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
\end{equation}
}}

We must note, that from (\ref{apprx_I_t0_t1}) and (\ref{R_ois_avg}) we can get an approximation for $R_{avg}(t_0,t_1)$

\hspace{2cm}
\fboxsep1em
\fbox{\parbox{335pt}
{
\begin{equation}\label{convexity_avg_ois_future}
R_{avg}(t_0,t_1) = \frac{\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
}}

Therefore, since $\log(1+x)\approx x$ we have that

\begin{equation*}
R_{avg}(t_0,t_1) \approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
\end{equation*}

@@

\begin{example}\label{example_convexity_hw_ois}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$. It is easy to show in the case of the Hull-White model
\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}\\
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
\end{align*}
Therefore we have that
\begin{align*}
\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
\end{align*}
Then if we substitute the last equality in (\ref{convexity_ois_future}) we get the convexity adjustment for OIS future. The next figure, show accuracy of (\ref{convexity_ois_future}) in the case of Hull-White

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

@@

>>>>

\begin{equation}\label{girsanov_spot_forward}

@@

D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 

@@

If we use (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that

@@

\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)

@@

Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future

@@

\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 

@@

\begin{example}\label{example_ca_future}
Let us to set 
\begin{align*}
g(T) &= \exp(-kT) \\
h(t) &= \sigma
\end{align*}
\end{example}
With this parametrization, the Cheyette model is equiavalent to Hull-White model. Also, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}\\
\end{align*}
Then it easy to show that the convexity adjustment (\ref{ca_approximation_futures}) is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}
\newpage
In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
\begin{align*}
R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
\end{align*}
We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}$ that will observable during whole period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales  
\begin{align*} 
\bar{R}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}
We must do several obeservations. The first observation is that, if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
\end{align*}
The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
\end{equation}
The second observation, is that under the dyam we must do is that
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
\end{equation}
In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
\begin{equation*}
I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
\end{equation*}
If we take $D_s$ on $I(t_0,t_1)$ we have that
\begin{equation*}
D_sI(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
\end{equation*}
Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
\begin{align}\label{apprx_I_t0_t1}
I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
\end{align}
Then, using the previous approximation, we get that
\begin{align*}
1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
\end{align*}
where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
Since, the Girsanov's theorem (see (\ref{girsanov_spot_forward}))
\begin{equation}\label{representation_i_0_t}
1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{ \Gamma^{2}(s,t_0,t_1)}{2} ds\right)
\end{equation}
Therefore

\hspace{2cm}
\fboxsep1em
\fbox{\parbox{335pt}
{
\begin{equation}\label{convexity_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
\end{equation}
}}
In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
\begin{equation*}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
\end{equation*}
Then from (\ref{representation_i_0_t}) we get that
\begin{equation}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
The last step, is to use the basic inequality $\log(1+x) \approx x$
when $x \approx 0$. If we do that, we get the next approximation for $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$

\fboxsep1em
\fbox{\parbox{300pt}
{
\begin{equation*}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
\end{equation*}
}}

@@

\begin{example}\label{example_convexity_hw_ois}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$. It is easy to show in the case of the Hull-White model
\begin{align*}
\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
\end{align*}
Therefore we have that
\begin{align*}
\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
\end{align*}
Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$. The next figure, show accuracy of (\ref{convexity_ois_future}) for the particular case of a Hull-White model.

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

@@

\subsection{CMSs}
In this last section we will study convexity adjustment for a CMS. Let us to introduce some notation, we will use it throughout the section. We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, we will define the OIS swap rate as
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
Now, we suppose that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore, we we have to take into consideration the effect to compute the expected value of $S_{a,b}(T_a)$ in a measure which is not its natural measure. Then, the convexity adjustment for a CMS is
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
After some changes of measure, it is easy to show that
\begin{align}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \nonumber \\
&= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right)
\end{align}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. It is common practice to assume that $M(T_a,T_p)$ is a funtion of the swap rate $S_{a,b}(T_a)$ i.e   $M(T_a,T_p)=f(S_{a,b}(T_a))$. The function $f(\cdot)$ is known as mapping function, and there is a vast literatura about how to choose it (see Piterbarg Volumen III, Hagan paper convexity withour replication). We will, try to do an approach, without to specify any mapping function.

where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
\begin{equation} \label{clark_ocone_swap_m}
M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{equation}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}\label{cms_first_order_convexity}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
=&  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
\approx&  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
\end{align}

\begin{example}
In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$. In the case of a Hull-White model, we have that
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore (\ref{cms_first_order_convexity}) is equal to
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
\end{equation*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$
